\section{Noetherian Rings}

\begin{exercise}\label{ex7.1}
	
\end{exercise}

\begin{exercise}\label{ex7.2}
	
\end{exercise}

\begin{exercise}\label{ex7.3}
	\begin{enumerate}
		\item[(i) $\Rightarrow$ (ii)] Use \Cref{4.8} and \Cref{4.4}.
		\item[(ii) $\Rightarrow$ (iii)] Let $S=\left\{1,x,x^2,\cdots\right\}$. Proof that $\bigcup\left(\mathfrak{a}:x^n\right)=S(\mathfrak{a})$.
		\item[(iii) $\Rightarrow$ (i)] Similar to the proof of \Cref{7.12}.
	\end{enumerate}
\end{exercise}

\begin{exercise}\label{ex7.4}
	
\end{exercise}

\begin{exercise}\label{ex7.5}
	Use \Cref{ex5.12} and \Cref{7.8}.
\end{exercise}

\begin{exercise}\label{ex7.6}
	Hint.
\end{exercise}

\begin{exercise}\label{ex7.7}
	Use a.c.c..
\end{exercise}

\begin{exercise}\label{ex7.8}
	$A\cong A[x]/(x)$.
\end{exercise}

\begin{exercise}\label{ex7.9}
	Hint.
\end{exercise}

\begin{exercise}\label{ex7.10}
	$M[x]=M\otimes A[x]$, so it is a homomorphic image of $M\times A[x]$.
\end{exercise}

\begin{exercise}\label{ex7.11}
	Counter example is an infinite product $\prod\mathbb{Z}/2\mathbb{Z}$.
\end{exercise}

\begin{exercise}\label{ex7.12}
	By \hyperref[ex3.16]{\Cref*{ex3.16}(i)}, $\mathfrak{a}\mapsto\mathfrak{a}^e$ is injective. Then use a.c.c..
\end{exercise}

\begin{exercise}\label{ex7.13}
	Transfer the Noetherian property $B\rightarrow B_\mathfrak{p}\rightarrow B_\mathfrak{p}/\mathfrak{p}B_\mathfrak{p}$.
\end{exercise}

\begin{exercise}[\textcolor{red}{Hilbert's Nullstellensatz}]\label{ex7.14}
	The hint uses a method other than Rabinowitsch trick.
\end{exercise}

\begin{exercise}\label{ex7.15}
	Hint.
\end{exercise}

\begin{exercise}\label{ex7.16}
	Use \Cref{ex7.15}.
\end{exercise}

\begin{exercise}\label{ex7.17}
	
\end{exercise}

\begin{exercise}\label{ex7.18}
	
\end{exercise}

\begin{exercise}\label{ex7.19}
	
\end{exercise}

\begin{exercise}\label{ex7.20}
	\begin{enumerate}[label=(\roman*),ref=\theexercise(\roman*)]\crefalias{enumi}{exercise}
		\item $\Rightarrow$: Rigorous proof requires using induction on $\mathcal{F}_i$, where $\mathcal{F}_i$ is formed by applying complement $i$ times on the topology $\tau=\mathcal{F}_0$, and satisfies $\mathcal{F}_0\subseteq \mathcal{F}_1\subseteq\cdots\subseteq\mathcal{F}$.
		\item $\Rightarrow$: Use \Cref{ex1.19}.
	\end{enumerate}
\end{exercise}

\begin{exercise}\label{ex7.21}
	\begin{enumerate}
		\item[$\Rightarrow$:] Use \Cref{ex7.20}.
		\item[$\Leftarrow$:] Use hint. If $\overline{E\cap X_0}\neq X_0$, $E\cap\overline{E\cap X_0}\in\mathcal{F}$ by minimality, but $E\cap\overline{E\cap X_0}=E\cap X_0$. If $U_0\subseteq E\cap X_0$, let $U_0=U\cap X_0$ where $U$ is open in $X$, then $E\cap X_0=U_0\cup\left(E\cap U^c\cap X_0\right)$.
	\end{enumerate}
\end{exercise}

\begin{exercise}\label{ex7.22}
	If $U_0\subseteq E\cap X_0$, use the notations similar to \Cref{ex7.21}. $U^c\cap X_0$ is closed, so by minimality $E\cap U^c\cap X_0$ is open.
\end{exercise}

\begin{exercise}\label{ex7.23}
	Hint.
\end{exercise}

\begin{exercise}\label{ex7.24}
	Hint.
\end{exercise}

\begin{exercise}\label{ex7.25}
	Use \Cref{ex5.11,ex7.24}.
\end{exercise}

\begin{exercise}\label{ex7.26}
	
\end{exercise}

\begin{exercise}\label{ex7.27}
	
\end{exercise}