\section{Primary Decomposition}

\begin{exercise}
	Use \Cref{ex3.21} so $\operatorname{Spec}(A/\mathfrak{a})=V(\mathfrak{a})$.
\end{exercise}

\begin{exercise}
	Omitted.
\end{exercise}

\begin{exercise}
	For any element $x\in A$, $x(1-ax)=0\in\mathfrak{q}$.
\end{exercise}

\begin{exercise}
	Omitted.
\end{exercise}

\begin{exercise}
	Omitted.
\end{exercise}

\begin{exercise}
	
\end{exercise}

\begin{exercise}\label{ex4.7}
	Element-wise.
\end{exercise}

\begin{exercise}
	Use \Cref{ex4.7}.
\end{exercise}

\begin{exercise}
	(i) $\Leftarrow$: $x$ is contained in all prime ideal containing $(0:\mathfrak{a})$, so $x\in\sqrt{(0:\mathfrak{a})}$. (iii) We have a relation $(0:\mathfrak{a})\subseteq\bigcap\sqrt{(\mathfrak{q}_i:\mathfrak{a})}\subseteq\mathfrak{p}$. Then use minimality to proof that $\mathfrak{p}$ is an associated prime ideal.
\end{exercise}

\begin{exercise}
	(iv) doesn't hold.
\end{exercise}

\begin{exercise}\label{ex4.11}
	Note that $x\in S(\mathfrak{a})$ $\Leftrightarrow$ there exists an $s\in S$ such that $sx\in\mathfrak{a}$. Show that $S_\mathfrak{p}(0)$ is contained in all $\mathfrak{p}$-primary ideals.\par
	If $0=\bigcap\mathfrak{q}_i$ is minimal, $\sqrt{(0)}$ is the intersection of minimal prime ideals.
\end{exercise}

\begin{exercise}\label{ex4.12}
	Use \Cref{3.11}. Use \Cref{4.9} to show there are at most $2^n$ different $S(\mathfrak{a})$.
\end{exercise}

\begin{exercise}
	(i) Use \Cref{ex4.12}. (ii) Use \Cref{4.8} and \Cref{4.9}. (iii) Proof that $S_\mathfrak{p}\left(\mathfrak{p}^{(m)}\mathfrak{p}^{(n)}\right)=\mathfrak{p}^{(m+n)}$. (iv) $\Leftarrow$: Show that $\mathfrak{p}^{(n)}$ is the smallest $\mathfrak{p}$-primary ideal containing $\mathfrak{p}^n$.
\end{exercise}

\begin{exercise}
	Let $x\notin\mathfrak{q}$. If $ab\in(\mathfrak{q}:x)$ but $a\notin(\mathfrak{q}:x)$, we have $xab\in\mathfrak{q}$ but $xa\notin\mathfrak{q}$. Thus, $b\in(\mathfrak{q}:xa)=(\mathfrak{q}:x)$ by maximality, and therefore $(\mathfrak{q}:x)$ is prime.
\end{exercise}

\begin{exercise}
	
\end{exercise}

\begin{exercise}
	Use \Cref{3.11} and \Cref{4.9}.
\end{exercise}

\begin{exercise}
	Use hint.
\end{exercise}

\begin{exercise}
	(i) $\Rightarrow$ (L1): By \Cref{4.9}, $S_\mathfrak{p}(\mathfrak{a})=\bigcap\mathfrak{q}_i$. Pick $x\in S_\mathfrak{p}$, then $\mathfrak{q}_i=(\mathfrak{q}_i:x)$ by \Cref{4.4}. (i) $\Rightarrow$ (L2): Use \Cref{ex4.12}.
\end{exercise}

\begin{exercise}
	Use hint.
\end{exercise}