\chapter{Discrete Valuation Rings and Dedekind Domain}

\begin{proposition}{9.1}
	Let $A$ be a Noetherian domain of dimension 1. Then every non-zero ideal $\mathfrak{a}$ in $A$ can be uniquely expressed as a product of primary ideals whose radicals are all distinct.
\end{proposition}

\section*{DISCRETE VALUATION RINGS}

Let $K$ be a field. A \textcolor{orange}{discrete valuation} on $K$ is a mapping $v$ of $K^*$ onto $\mathbb{Z}$ such that
\begin{enumerate}[label=\textup{(\arabic*)},ref=\thepropositiontemp(\roman*)]\crefalias{enumi}{proposition}
	\item $v{xy}=v(x)+v(y)$;
	\item $v(x+y)\geqslant\min\left(v(x),v(y)\right)$.
\end{enumerate}
The set consisting of all $x\in K^*$ such that $v(x)\geqslant0$ called the \textcolor{orange}{valuation ring} of $v$.

An integral domain $A$ is a \textcolor{orange}{discrete valuation ring} if there is a discrete valuation $v$ of its field of fractions $K$ such that $A$ is the valuation ring of $v$.

\begin{proposition}{9.2}
	Let $A$ be a Noetherian local domain of dimension 1, $\mathfrak{m}$ its maximal ideal. Then the following are equivalent:
	\begin{enumerate}[label=\textup{(\roman*)},ref=\thepropositiontemp(\roman*)]\crefalias{enumi}{proposition}
		\item $A$ is a discrete valuation ring;
		\item $A$ is integrally closed;
		\item $\mathfrak{m}$ is a principal ideal;
		\item $\dim_k\left(\mathfrak{m}/\mathfrak{m^2}\right)=1$;
		\item Every non-zero ideal is a power of $\mathfrak{m}$;
		\item There exists $x\in A$ such that every non-zero ideal is of the form $\left(x^k\right)$ for $k\geqslant0$.
	\end{enumerate}
\end{proposition}

\section*{DEDEKIND DOMAINS}

\begin{theorem}{9.3}
	Let $A$ be a Noetherian local domain of dimension 1. Then the following are equivalent:
	\begin{enumerate}[label=\textup{(\roman*)},ref=\thepropositiontemp(\roman*)]\crefalias{enumi}{proposition}
		\item $A$ is integrally closed;
		\item Every primary ideal in $A$ is a prime power;
		\item Every local ring $A_\mathfrak{p}$ with $\mathfrak{p}\neq0$ is a discrete valuation ring.
	\end{enumerate}
	A ring satisfying the conditions is called a \textcolor{orange}{Dedekind domain}.
\end{theorem}

\section*{FRACTIONAL IDEALS}

Let $A$ be an integral domain, $K$ its field of fractions. An $A$-submodule $M$ of $K$ is a \textcolor{orange}{fractional ideal} of $A$ if $xM\subseteq A$ for some $x\neq0$.

An $A$-submodule $M$ of $K$ is an \textcolor{orange}{invertible ideal} if there exists a submodule $N$ of $K$ such that $MN=A$. Then $N=(A:M)$, and $M$ is finitely generated fractional ideal.

\begin{proposition}{9.6}
	For a fractional ideal $M$, the following are equivalent:
	\begin{enumerate}[label=\textup{(\roman*)},ref=\thepropositiontemp(\roman*)]\crefalias{enumi}{proposition}
		\item $M$ is invertible;
		\item $M$ is finitely generated and , for each prime ideal $\mathfrak{p}$, $M_\mathfrak{p}$ is invertible;
		\item $M$ is finitely generated and , for each maximal ideal $\mathfrak{m}$, $M_\mathfrak{m}$ is invertible;
	\end{enumerate}
\end{proposition}

\begin{theorem}{9.8}
	Let $A$ be an integral domain. Then $A$ is a Dedekind domain $\Leftrightarrow$ every non-zero fractional ideal of $A$ is invertible.
\end{theorem}
